Visualizing Contingency Tables

### 2006-12-11 trunk/vcd/paper/Handbook/hsc.Rnw
fixed 783 -> 1456 in all papers/vignettes
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@627 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

As a four-way example, we use the punishment data \cite{vcd:andersen:1991} 
from a study of the Gallup Institute in Denmark in 1979 about
the attitude of a random sample of 783 persons towards corporal
punishment of children (see Table~\ref{tab:punish}).      
\index{data!Danish corporal punishment}
The data consist of four variables: Attitude is a binary variable
indicating whether a person approves moderate punishment of children
(``moderate''), or refuses any punishment of children (``no'').
Memory indicates whether the person recalls having been
punished as a child. Education indicates the
highest level of education (elementary, secondary, high). Finally, 
age indicates the age group in years (15--24, 25--39, $40+$).

>>>>

As a four-way example, we use the punishment data \cite{vcd:andersen:1991} 
from a study of the Gallup Institute in Denmark in 1979 about
the attitude of a random sample of 1,456 persons towards corporal
punishment of children (see Table~\ref{tab:punish}).      
\index{data!Danish corporal punishment}
The data consist of four variables: Attitude is a binary variable
indicating whether a person approves moderate punishment of children
(``moderate''), or refuses any punishment of children (``no'').
Memory indicates whether the person recalls having been
punished as a child. Education indicates the
highest level of education (elementary, secondary, high). Finally, 
age indicates the age group in years (15--24, 25--39, $40+$).
